Towards a better predictive model from rest fMRI: benchmarks across multiple phenotypes

### 2017-06-12 rs_study/experiments/paper/paper.tex
Figures: plot distribution difference on regions and networks
Reorganized prediction scores learned using ICA on COBRE

\journal{NeuroImage}
\title{Towards a better predictive model of rest fMRI: benchmarks across
multiple phenotypes}

@@

% Start positive

% Introduce cross-validation
% State the problem
% Explain what I do, and our conclusion

% XXX: TODO: announce the content of the paper

@@

\subsection{Overview of the pipeline}
\autoref{fig:pipeline}  depicts  our  prediction  pipeline.  It  consists  of  four
steps: i) Definition  of  brain  regions  of  interest  (ROIs),
ii) Extraction  of  the  time  series  associated  with  these  ROIs,
iii) Estimation  of  FC  metrics  from  these  time  series,
iv) Connectivity-based classification of the phenotypic target.
\subsection{Definition of brain regions or networks}

@@

%begin{figure*}[t]
%   \setlength{\fboxsep}{0pt}%
%   \begin{minipage}[T]{.26\paperwidth}
%    \includegraphics[height=.28\paperwidth]{pipeline.pdf}%
%    \llap{\raisebox{.265\paperwidth}{%
%   \parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
%   \hspace*{-.15ex}\,\hspace{-2ex}}}}}%
%   \medskip
%   \end{minipage}
%   \caption{\textbf{Resting-state functional connectivity prediction pipeline}}
%
%   {\bfseries\sffamily 1} -- Defining Brain ROIs: involves using three
%   pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
%   - Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
%   methods - Linear decomposition models: Group Independent Component
%   Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
%   Clustering models: KMeans - Agglomerative with Ward criterion. For each
%   data-driven method, we build the atlas on training data ($75\%$) on each
%   split (n=100) and use this atlas for the consecutive step. 
%   %
%   {\bfseries\sffamily 2} -- Timeseries signal extraction: For each atlas or
%   ROIs, from Step 1 are used in extracting subject specific timeseries signals.
%   %
%   {\bfseries\sffamily 3} -- Parameterizing functional connectivity between
%   ROIs,  using  correlation,  partial  correlation  or  tangent  space
%   embedding
%   %
%   {\bfseries\sffamily 4} -- Supervised learning: Classifiers, a classification
%   model is built to predict groups with two linear classifiers, SVC ($\ell_{1}$ or
%   $\ell_{2}$ penalization) and ridge regression ($\ell_{2}$ penalization).
%   %
%   Cross-validation for 100 splits with $75\%$ training set and remaining
%   $25\%$ test is used in Step 4, classification setting and reported scores
%   are Receiver Operating Characteristic and Area Under the Curve (ROC-AUC)
%   \label{fig:pipeline}
%end{figure*}
%
%\paragraph{Spread out predictions in a public challenge}

@@

\begin{figure}
    \centerline{%
	\includegraphics[width=1.\linewidth]{figures/regions_nonregions_difference_distribution.pdf}%
    }%
    \caption[regions vs non regions]{\textbf{Which is better for prediction:
            Brain regions or Brain networks}
        For each atlas (ICA, DictLearn, KMeans and BASC), we show here the
        best setting for prediction by measuring its impact on prediction
        accuracy for each dataset.

>>>>

\journal{NeuroImage}
\title{Towards a better predictive model from rest fMRI: benchmarks across
multiple phenotypes}

@@

@@

%\subsection{Resting State fMRI (rs-fMRI) prediction pipeline}
\autoref{fig:pipeline}  depicts  our  prediction  pipeline consists of
defining brain ROIs, connectivity parameterization and classification using
machine learning. We used this pipeline to study the various choices
at each
step by measuring the impact of each choice made across diverse prediction
tasks from five different rs-fMRI datasets. In below sections, we outline
about the choices used at each step, rs-fMRI datasets with the prediction task
in each dataset and cross-validation framework to prediction accuracy.

%trategy where at step i), we defined brain ROIs from training set of
%rs-fMRI images where the same set is used for training a linear
%model classifier in prediction tasks at step iii).
\subsection{Definition of brain regions of interest (ROIs)}
There exists many different approaches to define brain ROIs as overviewed
in \cite{thirion2014}. Here, we choose to
define brain ROIs using pre-defined brain atlases based on
anatomical and functional and using data-driven methods. For each type of
defining brain ROIs, we chose six variety of various
choices out of which three
pre-defined atlases - Automated Anatomical Labeling (AAL) - Harvard Oxford
- Bootstrap Analysis of Stable Clusters (BASC) and using four data-driven
methods - Linear decomposition models: Group Independent Component
Analysis (Group ICA) - Online Dictionary Learning (DictLearn) and
Clustering models: KMeans - Agglomerative with Ward criterion. For each
data-driven method, we build the atlas on training data ($75\%$) on each
split (n=100) and use this atlas for the consecutive step.

@@

\begin{figure*}[tb]
   \setlength{\fboxsep}{0pt}%
   \begin{minipage}[T]{.26\paperwidth}
    \includegraphics[height=.14\paperwidth]{figures/pipeline.pdf}%
    \llap{\raisebox{.11\paperwidth}{%
   \parbox{.28\paperwidth}{\colorbox{white}{\bfseries\sffamily
   \hspace*{-.15ex}\,\hspace{-2ex}}}}}%
   \medskip
   \end{minipage}
   \caption{\textbf{Resting-state functional connectivity prediction pipeline}
   Overview of the pipeline. Pipeline consists of three main steps:
   {\bfseries\sffamily 1}) defines brain regions (ROIs) from
   rs-fMRI images or using already defined reference atlases,
   {\bfseries\sffamily 2}) builds
   connectomes from time series signals extracted from these ROIs
   and {\bfseries\sffamily 3}) compares connectomes across subjects using supervised learning.
   The term connectome is referred to functional connectivity matrix between
   set of brain ROIs. In other words, we call this pipeline as connectome
   based prediction pipeline.}

  % {\bfseries\sffamily 2} -- Timeseries signal extraction: For each atlas or
  % ROIs, from Step 1 are used in extracting subject specific timeseries signals.
  % %
  % {\bfseries\sffamily 3} -- Parameterizing functional connectivity between
  % ROIs,  using  correlation,  partial  correlation  or  tangent  space
  % embedding
  % %
  % {\bfseries\sffamily 4} -- Supervised learning: Classifiers, a classification
  % model is built to predict groups with two linear classifiers, SVC ($\ell_{1}$ or
  % $\ell_{2}$ penalization) and ridge regression ($\ell_{2}$ penalization).
  % %
  % Cross-validation for 100 splits with $75\%$ training set and remaining
  % $25\%$ test is used in Step 4, classification setting and reported scores
  % are Receiver Operating Characteristic and Area Under the Curve (ROC-AUC)
   \label{fig:pipeline}
\end{figure*}
%
%\paragraph{Spread out predictions in a public challenge}

@@

\begin{figure}
    \centerline{%
	\includegraphics[width=1.\linewidth]{figures/regions_networks_difference_distribution.pdf}%
    }%
    \caption[regions vs non regions]{\textbf{Which is better for prediction:
            Brain regions or Brain networks}
        For each atlas (ICA, DictLearn, KMeans and BASC), we show here the
        best setting for prediction by measuring its impact on prediction
        accuracy for each dataset.
